Pool Model Paper

### 2023-12-04 pool_model.tex
Add references for spatial bacterial modelling

>>>>

- \ref{gorochowski_bsim_2012, li_nufeb_2019}: examples of other toolboxes for bacterial communities modelling.\\

In general, bacterial communities in 2D can experience collective motion called swarming~\ref{wu_collective_2015}.
Some works modelled 2D motile bacteria:\\
- \ref{decoene_microscopic_2011}: 2D chemostatic self-propelled bacterial motion of the flagellated bactreia (e.g. E. coli, B. subtilis).
Chemostaxis here was driven by the oxygen concentrations.

- \ref{rosser_modelling_2014}: modelling of the bacterial reorintation, rotation.

- \ref{sokolov_physical_2012, li_amplified_2008}: modelling of the bacteria using hydrodynamic interactions and Brownian motion.
Fluctuations in velocity and rotations.
(\ref{li_amplified_2008}: Brownian motion gives right motion observed using microscopy).

- \ref{farrell_mechanically_2013}: 2D modelling using Newtonian dynamics and only mechanical interactions + nutritient diffusion.
Diff limits where diffusion dominant and limits growth, and where it's irrelevant.
Mechanical pressure (due to bacteria-bacteria interactions) affects growth, can limit it.

- \ref{blanchard_bacterial_2015}: Modelled bacterial social interactions (toxins/public goods release) and its effect on the spatial structure.
